Appendix

### 2014-11-06 Rmarkdown/appendix.Rmd
Updated appendix

@@

In particular, in the case $n = 2$ we can compute the probability that two dependent but identically distributed Bernoulli random variables are equal, $Pr(X_{1} = X_{2}) = Pr(X_{1} = 0, X_{2} = 0) + Pr(X_{1} = 1, X_{2} = 1)$.

To extend the above result to the probability that two dependent but __non-identically__ distributed Bernoulli random variables are equal simply requires that we derive the appropriate transition matrix.

Let $X_{i} \eqd Bernoulli(p_{i})$ for $i = 1, 2$. The transition matrix, $\Pi = \bigl(\begin{smallmatrix}
Pr(X_{2} = x_{2} | X_{1} = x_{1}) \end{smallmatrix} \bigr)$, is given by

\begin{equation*}
\label{eq:transition_matrix_nid}
\Pi =
 \begin{pmatrix}
  (1 - p_{2}) + c p_{1} & p{2} - c p_{1} \\
  \big [ (1 - p_{2}) + c p_{1} \big ] (1 - p_{1}) & \big [ p_{2} + c (1 - p_{1}) \big ] p_{1}
 \end{pmatrix}
\end{equation*}

@@

\begin{align*}
Pr(X_{1} = X_{2}) &= Pr(X_{1} = 0, X_{2} = 0) + Pr(X_{1} = 1, X_{2} = 1) \\
                  &= Pr(X_{2} = 0 | X_{1} = 0) Pr(X_{0} = 0) +
                     Pr(X_{2} = 1 | X_{1} = 1) Pr(X_{0} = 1) \\
                  &= \big [ (1 - p_{2}) + c p_{1} \big ] (1 - p_{1}) + 
                     \big [ p_{2} + c ( 1 - p_{1}) \big ] p_{1} \\
                  &= (1 - p_{1}) (1 - p_{2}) + c p_{1} \big [1 - p_{1}] +
                     p_{1} p_{2} + c p_{1} (1 - p_{1}) \\
                  &= (1 - p_{1}) (1 - p_{2}) + p_{1} p_{2} + 2 c p_{1} (1 - p_{1})
\end{align*}

@@

Firstly, I download the data and unzip it:
```{r, cache = TRUE, message = FALSE}
library(R.utils)
library(data.table)
library(dplyr)

tmp <- tempdir()
url <- 'http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeHaibMethylRrbs/'
files <- paste0(url, 'wgEncodeHaibMethylRrbsHsmmtubefshdDukeSitesRep', 
                     1:3, '.bed.gz')
dests <- paste0(tmp,'/rep', 1:3, '.bed.gz')
x <- mapply(function(f, d) {
  download.file(f, d)
  gunzip(filename = d, overwrite = TRUE)
  fread(gsub(pattern = '.gz', replacement = '', x = d), sep = '\t')
  }, files, dests, SIMPLIFY = FALSE)
```

>>>>

provided that $max(1 - \frac{1}{p}, 1 - \frac{1}{1 - p}) \leq c \leq 1$.

@@

In particular, in the case $n = 2$ we can compute the probability that two 
dependent but identically distributed Bernoulli random variables are equal.

To extend the above result to the probability that two dependent and 
__non-identically__ distributed Bernoulli random variables are equal, simply 
requires that we derive the appropriate transition matrix. Switching notation 
to that used in Chapter \ref{chap:co-methylation_review}, let 
$Z_{h, i} \eqd Bernoulli(p_{h})$ and $Z_{h', i'} \eqd Bernoulli(p_{h'})$. The 
transition matrix, 
$\Pi = \bigl(\begin{smallmatrix} 
Pr(Z_{h', i'} = z_{h', i'} | Z_{h, i} = z_{h, i}) 
\end{smallmatrix} \bigr)$, is given by

\begin{equation*}
\label{eq:transition_matrix_nid}
\Pi =
 \begin{pmatrix}
  (1 - p_{h'}) + c p_{h} & p_{h'} - c p_{h} \\
  \big [ (1 - p_{h'}) + c p_{h} \big ] (1 - p_{h}) & \big [ p_{h'} + c (1 - p_{h}) \big ] p_{h}
 \end{pmatrix}
\end{equation*}

@@

\begin{align*}
Pr(Z_{h, i} = Z_{h', i'}) &= Pr(Z_{h, i} = 0, Z_{h', i'} = 0) + Pr(Z_{h, i} = 1, Z_{h', i'} = 1) \\
                  &= Pr(Z_{h', i'} = 0 | Z_{h, i} = 0) Pr(X_{0} = 0) +
                     Pr(Z_{h', i'} = 1 | Z_{h, i} = 1) Pr(X_{0} = 1) \\
                  &= \big [ (1 - p_{h'}) + c p_{h} \big ] (1 - p_{h}) +
                     \big [ p_{h'} + c ( 1 - p_{h}) \big ] p_{h} \\
                  &= (1 - p_{h}) (1 - p_{h'}) + c p_{h} \big [1 - p_{h}] +
                     p_{h} p_{h'} + c p_{h} (1 - p_{h}) \\
                  &= (1 - p_{h}) (1 - p_{h'}) + p_{h} p_{h'} + 2 c p_{h} (1 - p_{h})
\end{align*}

@@

Firstly, I download the data and unzip it:
```{r, cache = FALSE, message = FALSE}
library(R.utils)
library(data.table)
library(dplyr)
print(getwd())
```

```{r, cache = FALSE, message = FALSE}
dl_dir <- 'downloads/'
url <- 'http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeHaibMethylRrbs/'
files <- paste0('wgEncodeHaibMethylRrbsHsmmtubefshdDukeSitesRep',
                1:3, '.bed.gz')
dests <- paste0(dl_dir, files)
x <- mapply(function(f, d) {
  if (!file.exists(gsub(".gz", "", paste0(dl_dir, f)))) {
    download.file(url = paste0(url, f), d)
    gunzip(filename = d, overwrite = TRUE)
    }
  fread(gsub(pattern = '.gz', replacement = '', x = d), sep = '\t', 
        verbose = FALSE)
  }, files, dests, SIMPLIFY = FALSE)
```
